Mining Scenario/Transaction Pairs in HW/SW Co-verification Using Symbolic Execution

### 2017-04-06 paper.tex
soc figure

Thus, a transaction level property follows implication structure -- the 
antecedent of the implication is an event in $\mathcal{ST}$ or 
$\mathcal{HT}$ and the consequent is an event in $\mathcal{HT}$ 
or $\mathcal{ST}$ respectively.  An event in $\mathcal{ST}$ may be 
a function call or an update to program variables. Similarly, an event in 
$\mathcal{HT}$ corresponds to an update of combinational or sequential 
elements. Table~\ref{figure:transaction} shows few examples of transaction 
level property, written as monitors in C, for the UART IP.  In $monitor\_P1()$, 
$outb(UART\_TR,0x0c)$ is a FW event and $ack\_o$ is a HW event. Whereas in
$monitor\_P2$, the antecedent $tx\_empty()$ is a HW event and $send\_data$ is a FW
event. 
%
\begin{figure}[htbp]
\scriptsize
\begin{tabular}{l|l}
\hline
\multicolumn{2}{c}{Monitors (in C)}
\\
\hline
\begin{lstlisting}[mathescape=true,language=C,moredelim={[is][keywordstyle]{@@}{@@}}]
int monitor_P1() { 
 if(outb(UART_TR,0x0c)){
  next_timeframe();
  assert(@@ ack_o==1 @@);}}
\end{lstlisting} 
&
\begin{lstlisting}[mathescape=true,language=C,moredelim={[is][keywordstyle]{@@}{@@}}]
int monitor_P2() { 
 assert(!tx_empty() || 
 (@@(send_data&0x1)==1)@@);
}
\end{lstlisting} \\ 
\hline
\end{tabular}
\caption{Transaction-level property as monitor (in C)}
\label{figure:transaction}
\end{figure}
%

%-------------------------------------------------------------------------------
\subsection{Component level Property}
%-------------------------------------------------------------------------------
A {\em component level} property ($\psi_{c}$) is defined purely at the 
level of individual components of a co-design system. Recall that a component 
may be a HW model, a SW model or an interface model which contains only the 
interface logic.  A component-level property captures the design intent of a 
component in terms of its input/output behaviors.  This type of property 
is useful in a co-design environment for verifying individual components.   
Note that unlike the structure of $\psi_{t}$ which requires the antecedent 
or consequent to be a HW or SW event,  $\psi_{c}$ only contains signals 
(ports) or variables of a particular component.  Table~\ref{figure:component} 
shows an example of component level property for the UART HW only.  The 
System Verilog Assertion (SVA) is shown in the left and the equivalent 
monitor in C is shown in right.  
%
\begin{figure}[htbp]
\scriptsize
\begin{tabular}{l|l}
\hline
System Verilog Assertions  & Monitor (in C)
\\
\hline
\begin{lstlisting}[mathescape=true,language=Verilog]
P3: assert property 
 (@(posedge clk) 
 ack == 1|-> 
 (valid == 1 && 
 ##2 empty == 0)); 
\end{lstlisting}
&
\begin{lstlisting}[mathescape=true,language=C]
Bool monitor_P3() {
 assert(!ack || valid);
 next_timeframe();
 next_timeframe();
 assert(empty==0); }
\end{lstlisting} \\
\hline
\end{tabular}
\caption{Component-level property (in SVA) as monitor (in C)}
\label{figure:component}
\end{figure}
% 
%===============================================================================
\section{Experimental Results}
%===============================================================================
%
We report experimental results for FW-HW co-verification of a UART IP and a
SoC design.  All our experiments were performed on an Intel Xeon 3.07\,GHz
machine with 48\,GB RAM.  All times reported are in seconds.  The timeout 
for all our experiments was set to 2~hours.  
%

@@

\textbf{\emph{About the SoC:}}
%
We obtained an open source SoC design
from~\cite{DBLP:conf/fmcad/SubramanyanVRM15}.  It consists of an 8051
micro-controller, a memory arbiter, an external memory (XRAM) and
cryptographic accelerators.  The design statistics for SoC is given in
Table~\ref{table:stats}.  The accelerator implements encryption/decryption 
using the Advanced Encryption Standard (AES).  There is a separate 
module that interfaces the AES to the 8051 micro-controller using 
a memory-mapped I/O interface.  The micro-controller communicates 
with the accelerators and the XRAM by reading or writing to 
XRAM addresses.  The arbitration of these module is done by 
the memory arbiter module.

\Omit{
We synthesized the SoC to a software netlist (in C).  The generated model 
is bit-precise as well as cycle accurate.  The size of the
software netlist is approximately~3200 LOC.  The combinatorial exchanges
between the memory arbiter, XRAM and the AES module is modelled
appropriately in the software netlist.
}

@@

% ===============================================================================
\section{Limitations of Proposed Approach}
% ===============================================================================
The primary motivation for constructing a sequential single threaded unified 
co-verification model is to avoid enumerating exponential number of interleavings 
between the HW and FW threads.  We have shown that this is extremely beneficial for 
co-designs that exhibits producer-consumer relationship.  
In particular, our path-based algorithm in \verifox is able to suitably exploit 
this interaction behavior in a sequential co-verification model through symbolic 
execution which generates relevant scenario/transaction pairs.  However, this approach 
is not applicable for co-designs that exhibits true concurrency~\cite{concurrency}, 
that is, a FW its interacting HW threads does not show producer-consumer relationship.  
In this case, it is imperative to consider all possible interleavings between
these threads in some effecient manner.  However, our experience is that such 
co-designs occurs rarely in practise.

>>>>

Thus, a transaction level property follows implication structure -- the 
antecedent of the implication is an event in $\mathcal{ST}$ or 
$\mathcal{HT}$ and the consequent is an event in $\mathcal{HT}$ 
or $\mathcal{ST}$ respectively.  An event in $\mathcal{ST}$ may be 
a function call or an update to program variables. Similarly, an event in 
$\mathcal{HT}$ corresponds to an update of combinational or sequential 
elements. Figure~\ref{figure:transaction} shows an example of transaction 
level property, written as monitors in C, for the UART IP.  In $monitor\_P1()$, 
$outb(UART\_TR,0x0c)$ is a FW event and $ack\_o$ is a HW event. Whereas in
$monitor\_P2()$, the antecedent $tx\_empty()$ is a HW event and $send\_data$ is a FW
event. 
%
\begin{figure}[htbp]
\scriptsize
\begin{tabular}{l|l}
\hline
\multicolumn{2}{c}{Monitors (in C)}
\\
\hline
\begin{lstlisting}[mathescape=true,language=C,moredelim={[is][keywordstyle]{@@}{@@}}]
int monitor_P1() { 
 if(outb(UART_TR,0x0c)){
  next_timeframe();
  assert(@@ ack_o==1 @@);}}
\end{lstlisting} 
&
\begin{lstlisting}[mathescape=true,language=C,moredelim={[is][keywordstyle]{@@}{@@}}]
int monitor_P2() { 
 assert(!tx_empty() || 
 (@@(send_data&0x1)==1)@@);
}
\end{lstlisting} \\ 
\hline
\end{tabular}
\caption{Transaction-level property as monitor (in C)}
\label{figure:transaction}
\end{figure}
%

%-------------------------------------------------------------------------------
\subsection{Component level Property}
%-------------------------------------------------------------------------------
A {\em component level} property ($\psi_{c}$) is defined purely at the 
level of individual components of a co-design system. Recall that a component 
may be a HW model, a SW model or an interface model which contains only the 
interface logic.  A component-level property captures the design intent of a 
component in terms of its input/output behaviors.  This type of property 
is useful in a co-design environment for verifying individual components.   
Note that unlike the structure of $\psi_{t}$ which requires the antecedent 
or consequent to be a HW or SW event,  $\psi_{c}$ only contains signals 
(ports) or variables of a particular component.  Figure~\ref{figure:component} 
shows an example of component level property for the UART HW only.  The 
System Verilog Assertion (SVA) is shown in the left and the equivalent 
monitor in C is shown in right.  
%
\begin{figure}[htbp]
\scriptsize
\begin{tabular}{l|l}
\hline
System Verilog Assertions  & Monitor (in C)
\\
\hline
\begin{lstlisting}[mathescape=true,language=Verilog]
P3: assert property 
 (@(posedge clk) 
 ack == 1|-> 
 (valid == 1 && 
 ##2 empty == 0)); 
\end{lstlisting}
&
\begin{lstlisting}[mathescape=true,language=C]
Bool monitor_P3() {
 assert(!ack || valid);
 next_timeframe();
 next_timeframe();
 assert(empty==0); }
\end{lstlisting} \\
\hline
\end{tabular}
\caption{Component-level property (in SVA) as monitor (in C)}
\label{figure:component}
\end{figure}
% 
%===============================================================================
\section{Experimental Results}
%===============================================================================
%
We report experimental results for FW-HW co-verification of a UART IP and a
SoC design.  All our experiments were performed on an Intel Xeon 3.07\,GHz
machine with 48\,GB RAM.  All times reported are in seconds.  The timeout 
for all our experiments was set to 2~hours.  
%

@@

\textbf{\emph{About the SoC:}}
%
We obtained an open source SoC design
from~\cite{DBLP:conf/fmcad/SubramanyanVRM15}.  It consists of an 8051
micro-controller, a memory arbiter, an external memory (XRAM) and
cryptographic accelerators, as shown in Figure~\ref{fig:soc}.  
The design statistics for SoC is given in
Table~\ref{table:stats}.  The accelerator implements encryption/decryption 
using the Advanced Encryption Standard (AES).  There is a separate 
module that interfaces the AES to the 8051 micro-controller using 
a memory-mapped I/O interface.  The micro-controller communicates 
with the accelerators and the XRAM by reading or writing to 
XRAM addresses.  The arbitration of these module is done by 
the memory arbiter module.  
%
\begin{figure}[t]
\scalebox{.50}{\import{figures/}{soc.pspdftex}}
  \caption{SoC Design obtained from~\cite{DBLP:conf/fmcad/SubramanyanVRM15}
\label{fig:soc}}
\end{figure}
%
\Omit{
We synthesized the SoC to a software netlist (in C).  The generated model 
is bit-precise as well as cycle accurate.  The size of the
software netlist is approximately~3200 LOC.  The combinatorial exchanges
between the memory arbiter, XRAM and the AES module is modelled
appropriately in the software netlist.
}

@@

% ===============================================================================
\section{Limitations of Proposed Approach}
% ===============================================================================
The primary motivation for constructing a sequential single threaded unified 
co-verification model is to avoid enumerating exponential number of interleavings 
between the HW and FW threads.  We have shown that this is extremely beneficial for 
co-designs that exhibits producer-consumer relationship.  
In particular, our path-based algorithm in \verifox is able to suitably exploit 
this interaction behavior in a sequential co-verification model through symbolic 
execution which generates relevant scenario/transaction pairs.  However, this approach 
is not applicable for co-designs that exhibits true concurrency~\cite{concurrency}, 
that is, a FW its interacting HW threads do not show producer-consumer relationship.  
In this case, it is imperative to consider all possible interleavings between participating 
threads in an effecient manner.  However, our experience is that such 
co-designs occurs rarely in practise.
